Handovers - SIPHER 7 Equivalent Income

### 2023-06-21 minos/testing/education_transitions.Rmd
Various tweaks to the labour and education modules, and additional plots for education_transitions.Rmd and handovers_S7.Rmd

- [ ] Check what age people achieve each level of education
- [ ] Average age plot (see if change over time in raw)
  - [ ] Histograms
  - [ ] Animated histograms?
- [ ] Force labour_state to FT education until max_educ has been reached (this might already have been done)
- [ ] Change labour_state prediction to only run for those who have reached max_educ
- [ ] Check how many people move into FT education after age of 30
- [ ] Make sure stock population is doing max_educ prediction

@@

Mean ages.

@@

@@

>>>>

- [x] Check what age people achieve each level of education
  - [x] Average age plot (see if change over time in raw)
  - [x] Histograms
  - [ ] Animated histograms?
- [ ] Force labour_state to FT education until max_educ has been reached (this might already have been done)
- [ ] Change labour_state prediction to only run for those who have reached max_educ
- [ ] Check how many people move into FT education after age of 30
- [x] Make sure stock population is doing max_educ prediction

@@

## Mean ages

@@

## Transition into FT Education

How many people transition into full time education? How many do this after the age of 30?

```{r}
raw.eductrans <- raw.dat %>%
  select(pidp, time, age, education_state, max_educ, S7_labour_state) %>%
  mutate(backInEduc = (S7_labour_state == 'FT Education') & (lag(S7_labour_state, order_by = time) != 'FT Education')) %>%
  filter(backInEduc == TRUE)

ggplot(raw.eductrans, aes(x = age)) +
  geom_histogram() +
  labs(title = 'Age came back to FT Education')
```

@@

## Retirement

Test that retirement is working as planned. Make sure that all 65+ are in the not working category in outputs.

```{r}
retired <- base.dat %>%
  select(pidp, time, age, S7_labour_state) %>%
  filter(age >= 65) %>%
  group_by(S7_labour_state) %>%
  count()

ggplot(retired, aes(x = S7_labour_state, y = n)) +
  geom_col()

retired.by.ageGroup <- base.dat %>%
  select(pidp, time, age, S7_labour_state) %>%
  filter(age >= 65) %>%
  mutate(age.group = cut(age, breaks = 0,65,70,75,80,85,90,120)) %>%
  group_by(age.group, S7_labour_state) %>%
  count()

#ggplot(retired, aes(x = S7_labour_state, y = n)) +
#  geom_col()

### 2023-06-21 minos/validation/handovers_S7.Rmd
Various tweaks to the labour and education modules, and additional plots for education_transitions.Rmd and handovers_S7.Rmd

spaghetti_plot(income.spag, 'hh_income',
               save = shall.we.save,
               save.path = save.path)

@@

spaghetti_plot(base.ei, 'equivalent_income')

spaghetti_plot(ei.spag, 'equivalent_income',
               save = shall.we.save,
               save.path = save.path)

@@

spaghetti_plot(spag, 'S7_housing_quality',
               save = shall.we.save,
               save.path = save.path)

@@

spaghetti_plot(spag, 'S7_neighbourhood_safety',
               save = shall.we.save,
               save.path = save.path)

@@

spaghetti_plot(spag, 'S7_physical_health',
               save = shall.we.save,
               save.path = save.path)

@@

spaghetti_plot(spag, 'S7_mental_health',
               save = shall.we.save,
               save.path = save.path)

@@

spaghetti_plot(spag, 'loneliness',
               save = shall.we.save,
               save.path = save.path)

>>>>

#spaghetti_plot(income.spag, 'hh_income',
#               save = shall.we.save,
#               save.path = save.path)

@@

#spaghetti_plot(base.ei, 'equivalent_income')

#spaghetti_plot(ei.spag, 'equivalent_income',
#               save = shall.we.save,
#               save.path = save.path)

@@

#spaghetti_plot(spag, 'S7_housing_quality',
#               save = shall.we.save,
#               save.path = save.path)

@@

#spaghetti_plot(spag, 'S7_neighbourhood_safety',
#               save = shall.we.save,
#               save.path = save.path)

@@

#spaghetti_plot(spag, 'S7_physical_health',
#               save = shall.we.save,
#               save.path = save.path)

@@

#spaghetti_plot(spag, 'S7_mental_health',
#               save = shall.we.save,
#               save.path = save.path)

@@

#spaghetti_plot(spag, 'loneliness',
#               save = shall.we.save,
#               save.path = save.path)
